NFC and burnout in teachers - A replication and extension study

### 2021-08-30 Manuscript/Manuscript.Rmd
added multicorrelation plot

library(here)
library(tidyverse)
library(ggplot2)
library(lavaan)
library(psych)
library(MVN)
library(MBESS)
library(Hmisc)
library(kableExtra)
library(knitr)

@@

>>>>

library(here)
library(tidyverse)
library(ggplot2)
library(lavaan)
library(psych)
library(MVN)
library(MBESS)
library(Hmisc)
library(kableExtra)
library(knitr)
library(GGally)                 # from ggplot2, for multi-correlation plots

@@

```
```{r objective2_troubleshooting, echo=FALSE, message=FALSE, warning=FALSE}

# This function was taken from an answer on a Stackoverflow question on August 30th 2021
# https://stackoverflow.com/questions/35085261/how-to-use-loess-method-in-ggallyggpairs-using-wrap-function/35088740

  my_fn <- function(data, mapping, pts=list(), smt=list(), ...){
    ggplot(data = data, mapping = mapping, ...) +
      do.call(geom_point, pts) +
      do.call(geom_smooth, smt)
  }

# Plot a big correlational matrix to check for non-linear associations that might have caused the bad model fit
  ggpairs(score_data[,c(2,3,4,5,9,10,15,19,23,27)], lower = list(continuous = my_fn))
